Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-21 paper/main.tex
done with Wes pass for Tuesday

@@

\subsection{Machine Learning Model}
\label{sec-model}

\emph{Pairing programs} For each PythonTutor user, we look at the sequence of
programs they attempted to run. Each program that crashes is paired with the next
program by that user which does not crash. Many programs do not make it to the
end of our data pipeline; here are the most common reasons:
\begin{itemize}
    \item The user submitted only programs that crash or only programs that do
    not crash, so we can't create any pairs for that user.
    \item The program is out of scope for PythonTutor. For
    example, the program imports forbidden libraries (like os), or the program
    runs in over 1000 execution steps.
    \item The proportion of the program that has changed between the buggy and
    fixed versions is more than a standard deviation above the mean.
\end{itemize}
We end up with \textasciitilde270,000 usable pairs of programs.

\emph{Models} The following descriptions of Logistic Regression, Decision Trees,
and MLP will have to be redone as they are copied from Learning to Blame.

@@

\item[RQ5]{FIXME clustering?}

@@

\subsection{Label}

The label we would ideally like to use would be whether or not a term is the
true source of the crash; that is, whether the correct way to fix the crash is
to edit this term. However, manually labeling terms in such a way would be
prohibitive on such a large dataset. And the whole point of this work is that
there does not yet exist a reliable way of pinpointing bugs automatically. Thus
we are forced to use a proxy for our desired label as follows. Many PythonTutor
users use the site in an iterative fashion: they start out by writing
a program that crashes, and then edit it until it no longer crashes. Thus for our
dataset, we consider only the crashing programs for which the same user later
ran a program that did not crash. We then run a tree-diff \cite{tree-diff}
between the program that crashes and the one that does not. Any terms in the
crashing program that appear in the diff are labeled as bugs. This is of course
not a perfect proxy for the label we want; see Threats to Validity.

\subsection{Data Set}

Our raw data consist of every Python 3 program that a user executed on
PythonTutor.com~\cite{Guo2013-vu} (not in ``live'' mode) during 2017, other
than those with syntax errors or undefined variables.  Each program which
crashes (throws an uncaught Python exception) is paired with the next
program (by the same user) that does not crash, under the assumption that
the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a
stddev above average), since these are most likely to be violations of that
assumption (i.e., the program that does not crash is unrelated to the
crashing program).

@@

\subsection{Threats to validity}

@@

\section{Related Work}
FIXME: This must all be rewritten or dropped, as it is directly copied from
my previous papers. It serves as a placeholder to indicate length and to
remind us of some Software Engineering bits we might cite.

>>>>

\pagestyle{plain}
\pagenumbering{arabic}

@@

\subsection{Machine Learning Model Generation}
\label{sec-model}

\fixme{
\emph{Models} The following descriptions of Logistic Regression, Decision Trees,
and MLP will have to be redone as they are copied from Learning to Blame.
}

@@

@@

\subsection{Dataset and Program Collection}

Our raw data consist of every Python 3 program that a user executed on
PythonTutor.com~\cite{Guo2013-vu} (not in ``live'' mode) during 2017, other
than those with syntax errors or undefined variables.  Each program which
crashes (throws an uncaught Python exception) is paired with the next
program (by the same user) that does not crash, under the assumption that
the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a
stddev above average), since these are most likely to be violations of that
assumption (i.e., the program that does not crash is unrelated to the
crashing program). We also discard submissions that are out of scope given
PythonTutor's policies (e.g., such as very long-running executions or the
use of forbidden libraries).

Ultimately, the dataset used in this evaluation contained just over
270,000 usable pairs of programs.

\subsection{Labeled Training and Ground Truth}

Our algorithm is based on supervised machine learning and thus requires
labeled training instances. In addition, our evaluations require a ground
truth notion of which terms correspond to correct fault localizations.

We use the terms changed involved in the fixes by actual users as our
ground truth and training information.  Many PythonTutor users use the site
in an iterative fashion: they start out by writing a program that crashes,
and then edit it until it no longer crashes. Our dataset contains only only
those crashing programs for which the same user later submitted a program
that did not crash. We compute a tree-diff \cite{tree-diff} between the
originaly, buggy submission and the first fixed submission. We define 
the ground truth correct answer to be the set of terms in the crashing
program that also appear in the diff. We discuss the implications of this
choice in \secref{threats}.

@@

\subsection{Threats to validity}
\label{sec-threats}

@@

\section{Related Work}
\fixme{This must all be rewritten or dropped, as it is directly copied from
my previous papers. It serves as a placeholder to indicate length and to
remind us of some Software Engineering bits we might cite.}
